Multicast File Transfer Protocol

### 2011-07-14 papers/paper1/paper.tex
Small changes

\section{Introduction}

@@

% jrw:  Move this to the introduction.
Moving data across a network can take a variety of forms. These forms correspond to different user needs and consequently different protocols. Multicast File Transfer Protocol (MFTP) addresses the need to move immutable data between many different nodes in a fully distributed network. 
%% This is useful for 1) device discovery 2) File transfer in the absence of many technologies (including internet). the only thing that is necessary is computers with routing and broadcast/multicast enabled 3) maximizing the reach of a gossip style network

@@

\section{I/O Automata Representation and Programming Model\label{representation}}

Conclude with our recommendations for programming, highlight need for exploration.

\section{Design and Implementation\label{design}}

\begin{itemize}
  \item Problem
  \item Design forces
  \item Solution
  \item Consequences
\end{itemize}

>>>>

\section{Introduction}
% jrw:  Move this to the introduction.
Moving data across a network can take a variety of forms. These forms correspond to different user needs and consequently different protocols. Multicast File Transfer Protocol (MFTP) addresses the need to move immutable data between many different nodes in a fully distributed network. 
%% This is useful for 1) device discovery 2) File transfer in the absence of many technologies (including internet). the only thing that is necessary is computers with routing and broadcast/multicast enabled 3) maximizing the reach of a gossip style network

@@

@@

%%TODO: Talk about validation

\section{Implementation}

%%TODO: Talk about validation - possible coinage 'incremental digest'

\paragraph{I/O Automata}
We used an I/O Automata framework to develop an implementation of the MFTP protocol.
General overview of the framework and formal model.
Describe our implementation at the 50k ft view and work our way done until things are no longer interesting.
Justin's picture:

The MFTP protocol is built off of an I/O Automata framework.  I/O Automata is *blank* (cite Nancy Lynch). The framework we used for our purposes is a C++ framework developed by Justin R. Wilson.

%%\begin{itemize}
%%  \item Problem
%%  \item Design forces
%%  \item Solution
%%  \item Consequences
%%\end{itemize}
